% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice. 

\documentclass{beamer}
\usepackage[absolute,overlay]{textpos}
\usepackage[timeinterval=1]{tdclock}


\usepackage{amssymb,amsmath,amsfonts,amsthm}
\usepackage{url}
\usepackage[backend=bibtex,style=verbose]{biblatex}
\footnotesize{\small}

\bibliography{s-arc-solCay.bib}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}


\usepackage{multirow}





\def\SL{\mathrm{SL}}
\def\GL{\mathrm{GL}}
\def\PSL{\mathrm{PSL}}
\def\PGL{\mathrm{PGL}}
\def\PSU{\mathrm{PSU}}
\def\PSp{\mathrm{PSp}}
\def\PO{\mathrm{P\Omega}}
\def\PGaL{\mathrm{P\Gamma L}}
\def\PSigU{\mathrm{P\Sigma U}}
\def\AGaL{\mathrm{A\Gamma L}}
\def\Aut{\mathrm{Aut}}
\def\Inn{\mathrm{Inn}}
\def\Out{\mathrm{Out}}
\def\Cay{\mathrm{Cay}}
\def\val{\mathrm{val}}
\def\HS{\mathrm{HS}}
\def\PH{\mathcal{PH}}
\def\GI{\mathcal{GI}}
\def\PG{\mathrm{PG}}
\def\soc{\mathrm{soc}}
\def\proof#1{\textbf{Proof.}{#1}\qed}


\def\TWthm{\begin{theorem}[2.2, Thompson-Wielandt]
Let $\Gamma$ be a connected $(G, s)$-transitive graph with $s\geq  2$, and let $\alpha$ and $\beta$ be adjacent vertices of $\Gamma$. Then one of the following holds, where p is a prime:
\begin{enumerate}
	\item $s\leq 3$, $G_{\alpha\beta}^{[1]}=1$, and $G_{\alpha}^{[1]}\cong(G_{\alpha}^{[1]})^{\Gamma(\beta)}\triangleleft G_{\alpha\beta}^{\Gamma(\beta)}\cong G_{\alpha\beta}^{\Gamma(\alpha)}$;
	\item $s\leq 3$, $G_{\alpha\beta}^{[1]}$ is a nontrivial p-group, $\PSL_d(p^f)\triangleleft G_\alpha^{\Gamma(\alpha)}$ for some $d\geq 2$, and $\val(\Gamma)=(p^{df}-1)/(p^f-1)$;
	\item $s\geq 4$, $\PGL_2(p^f)\triangleleft G_\alpha^{\Gamma(\alpha)}$, $\val(\Gamma)=p^f+1$, and one of the following occurs:
	\begin{enumerate}[i]
		\item s=4, and $G_\alpha=p^{2f}:\frac{p^f-1}{(3,p^f-1)}.\PGL_2(p^f).\mathcal{O}$ with $|\mathcal{O}|\mid (3,p^f-1)f$;
		\item s=5, and $G_\alpha=p^{3f}:\GL_2(2^f).\mathbb{Z}_e$ with $e|f$;
		\item s=7, and $G_\alpha=(p^{2f}\times (p^f)^{1+2}):\GL_2(3^f).\mathbb{Z}_e$ with $e|f$.
	\end{enumerate}
\end{enumerate}
\end{theorem}}

\def\Lem2.3{\begin{lemma}[2.3]
For a connected $(G,3)$-arc-transitive graph $\Gamma$ and adjacent vertices $\alpha,\beta$, at least one of the following holds: \footcite{LI2015331}\textsuperscript{,Thm 4.2}
\begin{enumerate}
	\item $G_\alpha^{[1]}$ is transitive on $\Gamma(b)\backslash\{\alpha\}$.
	\item $G_\alpha=A_7$ or $S_7$.
	\item $\mathbb{Z}_p^f\triangleleft G_\alpha^{\Gamma(\alpha)}\leq \AGaL_1(p^f)$ with p a prime.
\end{enumerate}
\end{lemma}}


\def\Lem2.5{\begin{lemma}[2.5]
Let $\Gamma$ be a connected $(G,s)$-transitive graph with $s\geq 3$, and suppose $N\triangleleft G$ and not semiregular. Then one of the following holds:
\begin{enumerate}
	\item both $G_\alpha^{\Gamma(\alpha)}$ and $N_\alpha^{\Gamma(\alpha)}$ are almost simple 2-transitive;
	\item $G_\alpha^{\Gamma(\alpha)}$ is affine and $N_\alpha^{\Gamma(\alpha)}$ is primitive.
\end{enumerate}
\end{lemma}}


\newtheorem{proposition}{Proposition}[theorem]


%%%%%%%%%%

%START

%%%%%%%%%%








\begin{document}


\title{s-Arc-transitive solvable Cayley graphs}
\setbeamerfont{subtitle}{size=\fontsize{8}{15}}
\subtitle{CAI HENG LI, JIANGMIN PAN, AND YINGNAN ZHANG}

% A subtitle is optional and this may be deleted
%\subtitle{PhD Thesis Defense}

\author{Speaker: Yuandong Li}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[BJTU] % (optional, but mostly needed)
{Beijing Jiaotong University}

% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date{\today}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

%\subject{Applied Math}
% This is only inserted into the PDF information catalog. Can be left
% out. 

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% t`	he beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}




% Let's get started


\begin{frame}
\titlepage
%\initclock
%\date[\initclock \cronominutes\timeseparator\cronoseconds]{}
\end{frame}
\date{\crono}


\begin{frame}{Outline}
 \tableofcontents
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.


\section{Preliminaries \& Background}

\begin{frame}{Preliminaries}
Let $\Gamma$ be a finite simple undirected graph. Let $G\leq \Aut\Gamma$.
\begin{definition}
	\begin{itemize}
		\item \textbf{s-arc:} (s+1)-tuple of vertices $\alpha_0,\alpha_1,\cdots,\alpha_s$ where $\alpha_i$ is adjacent to $\alpha_{i+1}$ and $\alpha_{j-1}\neq\alpha_{j+1}$ for $0\leq i\leq s-1$ and $1\leq j\leq s-1$.
		\item \textbf{(G,s)-arc-transitive:} $G$ is transitive on the set of s-arcs of $\Gamma$.
		\item \textbf{(G,s)-transitive:} (G,s)-arc-transitive but not (G,s+1)-arc-transitive.
	\end{itemize}
For short, \textbf{s-transitive} means $(\Aut\Gamma,s)$-transitive for graphs.
\end{definition}
\begin{lemma}
	\begin{itemize}
		\item s-arc-transitive ($1\leq s$) $\Longrightarrow$ k-arc-transitive ($1\leq k\leq s$).
		\item the s-arc-transitivity of a graph is inherited by the normal quotients.
	\end{itemize} 
\end{lemma}
\end{frame}

\begin{frame}{Preliminaries}
\begin{definition}
	\begin{itemize}
		\item \textbf{Cayley graph:} $\Cay(G,S)$ with vertex set $G$ and edges $yx^{-1}\in S$.
		\item \textbf{solvable Cayley graph:} $G$ is solvable.
	\end{itemize}
\end{definition}
\begin{lemma}
	\center $\Gamma$ is Cayley of $G$ $\iff$ $\exists G\lesssim \Aut\Gamma$ which is vertex-regular.
\end{lemma}
\end{frame}

\begin{frame}{Preliminaries}
\begin{definition}
	A transitive permutation group G is said to be \\\textbf{quasiprimitive} if its nontrivial normal subgroups are transitive, and \\\textbf{bi-quasiprimitive} if its nontrivial normal subgroups have at most 2 orbits and there exists one which has exactly 2 orbits.
\end{definition}

The O'Nan-Scott-Praeger theorem \footcite{praeger_1997} divides the quasiprimitive permutation groups into 8 types: holomorph affine (HA), holomorph simple (HS), holomorph compound (HC), almost simple (AS), simple diagonal (SD), compound diagonal (CD), product action (PA) and twisted wreath product (TW).
\end{frame}


\begin{frame}{Background}
\begin{itemize}
	\item 1947, Tutte: No 6-arc-transitive trivalent graphs.
	\item 1981, Weiss: No s-arc-transitive graphs with $\val\geq 3$ for $s=6$ and $s\geq 8$.
	\item 2019, Li C.H. \& Xia B.Z.: \\ Connected \textbf{non-bipartite} 3-arc-transitive solvable Cayley graph with $\val\geq 3$ is a normal cover of the Hoffman-Singleton graph or the Petersen graph.
	\item 2021, Zhou J.X.: No such normal covers, so $s\leq 2$ sharply.
\end{itemize}

\begin{problem}
Studying connected \textbf{bipartite} s-arc-transitive solvable Cayley graphs, and determining the upper bound on $s$.	
\end{problem}
For convenience, one may assume $s\geq 3$ and $\val\geq 3$. 

\end{frame}




\section{Main Result \& Examples}
\begin{frame}{Main Result}
\begin{theorem}
Every connected s-arc-transitive solvable Cayley graph with $s\geq 3$ and $val\geq 3$ is a normal cover of one of the following graphs:	
\begin{enumerate}
	\item the complete bipartite graph $K_{n,n}$ with $n\geq 3$;
	\item the geometry incidence graph $\mathcal{GI}(5, 2, 2)$;
	\item the standard double cover of the Hoffman-Singleton graph;
	\item a graph $\Sigma$ with valency $p^f+1$ such that $\PSL_3(p^f).2\leq \Aut\Sigma\leq \Aut(\PSL_3(p^f))$ and $\mathbb{Z}_p^{2f}:\SL_2(p^f)\triangleleft(\Aut\Sigma)_\alpha$, where $p^f\geq 3$ is a prime power and $\alpha$ is a vertex.
\end{enumerate}
In particular, the sharp upper bound on s is 4.
\end{theorem}
These normal covers are being investigated in a sequel. (usually challenge)
\end{frame}

\begin{frame}{Examples}
(1) $\mathbf{K}_{n,n}$ with $n\geq 3$
\begin{itemize}
	\item 3-transitive
	\item $\mathbf{K}_{n,n}\cong \Cay(G,G\backslash H)$ where $G$ is solvable and $H<G$ of index 2
\end{itemize}

(2) $\mathcal{GI}(5,2,2)$
\begin{itemize}
	\item the incidence graph of $(\mathcal{P,L})$ where $\mathcal{P}$(resp. $\mathcal{L}$) is the set of 2-subspace(resp. 3-subspace) of $\mathbb{F}_2^5$
	\item $\Aut(\GI(5,2,2))=\GL_5(2).\langle \sigma\rangle$ is vertex-transitive
	\item $G_\alpha=2^6:(\GL_2(2)\times\GL_3(2))$, $G_{\alpha\beta}=2^8:(S_3\times S_3)$, val=$\frac{|G_\alpha|}{|G_{\alpha\beta}|}$=7
	\item 3-transitive\footcite{LI20162907}$^\text{,Theorem 3.4}$
	\item $G=RG_\alpha$ with $R\cong 31:5:2$ vertex-regular\footcite{LI2022factorizations}$^\text{, Theorem 1.1}$
\end{itemize}

\end{frame}

\begin{frame}{Examples}
(3) $\HS_{50}^{(2)}$
\begin{itemize}
	\item $\HS_{50}$ is 3-transitive \\$\Aut(\HS_{50})=\PSigU(3,5)$ has a solvable vertex-transitive subgroup\\ It is NOT a Cayley graph
	\item \textbf{standard double cover:} $\Gamma^{(2)}=(\tilde{V},\tilde{E})$ of $\Gamma=(V,E)$, where\\ $\tilde{V}=V\times\{1,2\}$, $\tilde{E}=\{\{(v,1),(w,2)\}\mid\{v,w\}\in E\}$\\ $\Aut(\Gamma^{(2)})\geq \Aut\Gamma\times\langle\sigma\rangle$, $\Gamma$ s-arc-transitive $\implies$ $\Gamma^{(2)}$ s-arc-transitive
	\item By MAGMA, $\exists_1$ connected $G$-arc-transitive 7-valent graph $\Gamma$ of order 50 with $(G,G_\alpha)=(\PSU_3(5),A_7)$ or $(\PSU_3(5).\mathbb{Z}_2,S_7)$. $\Gamma\cong \HS_{50}$
	\item By MAGMA, $\exists_1$ connected $G$-arc-transitive 7-valent graph $\Gamma$ of order 100 with $(G,G_\alpha)=(\PSU_3(5).\mathbb{Z}_2,A_7)$. $\Gamma\cong \HS_{50}^{(2)}$
\end{itemize}
(\textcolor{red}{Q: Could a normal cover of $\HS_{50}^{(2)}$ be solvable Cayley?} see Zhou's paper)
\end{frame}

\begin{frame}{Examples}
(4) $\mathcal{PH}(3,q)$
\begin{itemize}
	\item the incidence graph of $\PG(2,q)=(\mathcal{P,L})$, where \\$\mathcal{P}$(resp. $\mathcal{L}$) is the set of 1-subspace(resp. 2-subspace) of $\mathbb{F}_q^3$
	\item $\Aut(\PH(3,q))=\PGaL_3(q).\langle \sigma\rangle=\Aut(\PSL_3(q))$
	\item $(\alpha_0,\cdots,\alpha_4)$ with $\alpha_0\in \mathcal{P}$ corresponds to a basis $v_1,v_2,v_3$ such that\[ \alpha_0=\langle v_1\rangle, \alpha_1=\langle v_1,v_2\rangle, \alpha_2=\langle v_2\rangle, \alpha_3=\langle v_2,v_3\rangle, \alpha_4=\langle v_3\rangle \]all ordered bases are equiv. under linear transformation\\$\implies$ 4-arc-transitive
	\item a Cayley graph\footcite{MARUSIC2003162} of $D_{2(q^2+q+1)}$, for example Heawood graph.
\end{itemize}
\end{frame}


\section{Proof of the Main result}

\subsection{Overview of the proof}

\begin{frame}{Overview of the proof}
	Let $\Gamma=\Cay(H,S)$ be connected, $(G,s)$-transitive, $\val\geq 3$,\\ with $H$ solvable, $H\leq G\leq \Aut\Gamma$, $s\geq 3$.
	
	Let $M\triangleleft G$ (may trivial) be maximal with $\geq 3$ orbits on $V\Gamma$.\\Then
	\begin{itemize}
		\item $\Gamma$ is a normal cover of $\Gamma_M$
		\item $\Gamma_M$ is $(G/M,s)$-arc-transitive
		\item $G/M$ is either quasiprimitive or bi-quasiprimitive on $V\Gamma_M$, $|V\Gamma_M|\geq 3$
	\end{itemize}

\begin{theorem}[Praeger,1993]
Let $\Gamma$ be a finite connected graph, $G\leq \Aut\Gamma$ is s-arc transitive on $\Gamma$ for some $s\geq 2$. Suppose $N\triangleleft G$ has more than two orbits on vertices. Then\begin{enumerate}
	\item $\Gamma_N$ is finite and connected and the group of automorphisms of $\Gamma_N$ induced by G is s-arc transitive on $\Gamma_N$.
	\item N is semiregular on vertices (that is $N_\alpha= 1$ for each vertex $\alpha$ of $\Gamma$) and $\Gamma$ is a cover of $\Gamma_N$. 
\end{enumerate}  
\end{theorem}

\end{frame}

\begin{frame}{Overview of the proof}
\textbf{Case quasiprimitive:} 
$\Gamma_M$ non-bipartite. By Li-Xia-Zhou, no such graphs.

\textbf{Case bi-quasiprimitive:} $\Gamma_M$ bipartite.

Then either $\Gamma_M=\mathbf{K}_{n,n}$, or $G/M$ is almost simple. \textcolor{blue}{(Reduce to AS type)}\\Moreover, $\soc(G/M)$ is a classical simple group of Lie type. \\\textcolor{blue}{(Use factorization of AS groups with a solvable factor)}

\ 

Let $s_0$ be the sharp upper bound on $s$.
\begin{itemize}
	\item By Example (4), $\PH(3,q)$ is 4-transitive, so $s_0\geq 4$.
	\item If there is a connected 5-arc-transitive solvable Cayley graph $\Gamma$, \\ then $\Gamma$ is a normal cover of a 5-arc-transitive graph of type (1)-(4),\\ while analysis above states no such graph. 
\end{itemize}
Hence $s_0=4$.
\end{frame}

\subsection{Reduce to almost simple groups} 
\begin{frame}{Reduce to almost simple groups}
In the remains of this talk, we assume the followings.

\begin{itemize}
	\item Let $\Gamma$ be a connected bipartite $(G,s)$-transitive graphs of val$\geq 3$, with bipartitions $\Delta_1$ and $\Delta_2$ and $s\geq 3$.
	\item Suppose $G$ is bi-quasiprimitive on $V\Gamma$ and contains a vertex-transitive solvable subgroup $H$. 
	\item Set $G^+=G_{\Delta_1}$, the setwise stabilizer of $G$ on $\Delta_1$, and $H^+=H\cap G^+$.
	\item Let $\alpha$, $\beta$ be adjacent vertices.
\end{itemize}

Some immediate facts:
\begin{itemize}
	\item $G^+=G_{\Delta_1}=G_{\Delta_2}$ has index 2 (hence normal) in $G$ and is transitive on both $\Delta_1$ and $\Delta_2$, as well as $H^+$ in $H$.
	\item $G=\langle G^+,g\rangle$ where $g\in G\backslash G^+$, $g$ interchanges $\Delta_1$ and $\Delta_2$, $g^2\in G^+$
\end{itemize}

\end{frame}


\begin{frame}{Case: unfaithful action}
Now we consider the action of $G^+$ on $\Delta_1$ and $\Delta_2$.
\begin{lemma}[4.2]
	If $G^+$ acts unfaithfully on $\Delta_1$ or $\Delta_2$, then $\Gamma=\mathbf{K}_{n,n}$, where $n=|V\Gamma |/2$.
\end{lemma}
\proof{
Let $K=\ker(G^+\curvearrowright\Delta_1)$. \\Then $K^g=\ker(G^+\curvearrowright\Delta_2)$ and $1\neq KK^g=K\times K^g\triangleleft G$.\\$\because$ $G$ is bi-quasiprimitive, $K\times K^g$ has at most 2 orbits.\\Since $K^g$ fixes $\Delta_2$ pointwise, $K$ must be transitive on $\Delta_2$.\\It follows that $\Gamma=\mathbf{K}_{n,n}$.}

\ 

We thus additionally assume $G^+$ is faithful on both $\Delta_1$ and $\Delta_2$.\[G^+\cong (G^+)^{\Delta_1}\cong (G^+)^{\Delta_2}\]
We will prove the above actions are quasiprimitive of almost simple type.
\end{frame}

\begin{frame}{Quasiprimitive $\implies$ same type AS or PA}
\begin{lemma}[4.3]
	Suppose $G^+$ is quasiprimitive on $\Delta_1$ or $\Delta_2$. Then \begin{enumerate}
		\item $G^+$ is quasiprimitive on both $\Delta_1$ and $\Delta_2$
		\item both $ (G^+)^{\Delta_1}$ and $ (G^+)^{\Delta_2}$ have the same type AS or PA
	\end{enumerate}
\end{lemma}
\proof{WLOG, assume $G^+$ is quasiprimitive on $\Delta_1$.\\$G$ transitive on $V\Gamma$ and $G^+\triangleleft G$ $\implies$ $G^+\curvearrowright\Delta_1$, $\Delta_2$ are perm. isom.\\Hence $G^+$ is quasiprimitive on $\Delta_2$ of the same type on $\Delta_1$.\\By ref.\footcite{GIUDICI2003analysing}\textsuperscript{,Thm 1.2}, $(G^+)^{\Delta_1}$ is of type HA, AS, TW or PA.\\For cases HA or TW, $\soc(G^+)\triangleleft G$ is regular on $\Delta_1$ and $\Delta_2$, \\then $\Gamma$ is a \textbf{G-normal bi-Cayley graph} on $\soc(G^+)$.\\By ref.\footcite{CONDER2020264}\textsuperscript{,Lem 3.2}, $\Gamma$ is at most $(G,2)$-arc-transitive, contradicting $s\geq 3$.}%\\Thereby, $G^+$ has the same type AS or PA on $\Delta_1$ and $\Delta_2$.}
\end{frame}


\begin{frame}{Study $\soc(G^+)$}
\begin{lemma}[4.4]
$\soc(G^+)$ is nonsolvable and is the the unique minimal normal subgroup of $G$, and $\soc(G^+)_\alpha\neq 1$.
\end{lemma}
\textbf{Proof.}{\\ If $G^+\curvearrowright\Delta_1$ is quasiprimitive. \\By lemma 4.3, $G^+$ is of type AS or PA.\\So $\soc(G^+)\mathop{\triangleleft}\limits_{min}G^+$ and is nonsolvable and not semiregular.\\ Let $C=C_G(\soc(G^+))$. Then $C\triangleleft G$ and $\soc(G^+)\cap C=Z(\soc(G^+))=1$.\\If $C\neq 1$, as $C\cap G^+=1$ and $G=G^+.2$, we derive that $C\cong \mathbb{Z}_2$.\\ Since $|V\Gamma|>4$, C has more than 2 orbits, contradicting G bi-quasiprimitive.\\Hence $C=1$ and $\soc(G^+)$ is also unique in $G$.
}
\end{frame}

\begin{frame}
Now assume $G^+$ is not quasiprimitive on both $\Delta_1$ and $\Delta_2$.\\ Then $\exists M\mathop{\triangleleft}\limits_{min} G^+$ acting intransitively on $\Delta_1$ hence has $> 2$ orbits on $V\Gamma$. Thus $M\not\triangleleft G$ and $M^g\neq M$. (Recall $G=\langle G^+,g\rangle$)\\Since $g^2\in G^+$, one has $MM^g=M\times M^g\leq G^+$ is normal in $G$.\\By bi-quasiprimitivity of $G$, $M\times M^g$ is transitive on $\Delta_1$ and $\Delta_2$.

By ref.\footcite{LI2002197}\textsuperscript{,Thm 1.5}, either
\begin{enumerate}[(a)]
	\item $M\times M^g$ is regular on $\Delta_1$ and $\Delta_2$; or
	\item $\soc(G^+)=M\times M^g$ is nonsolvable and not semiregular, and is the unique minimal normal subgroup of G.
\end{enumerate}
For case (b), done.\\
For case (a), $\Gamma$ is a G-normal bi-Cayley graph on $M\times M^g$, again by ref.\footcite{CONDER2020264}\textsuperscript{,Lem 3.2}, is at most $(G,2)$-arc-transitive. A contradiction.\qed 
\end{frame}



\begin{frame}{Structure of $\soc(G^+)$}
According to Lemma 4.4, we may set that
\[ N:=\soc(G^+)=T_1\times T_2\times\cdots\times T_d\cong T^d\mathop{\triangleleft}\limits_{min}^{unique} G . \]
Then $N$ is transitive on $\Delta_1$ and $\Delta_2$ since $G$ is bi-quasiprimitive.

\ 

Consider $G^+\curvearrowright \{T_1,\cdots,T_d\}$ by conjugation with kernel $K$.

Then $N\triangleleft K\leq \Aut(T_1)\times \cdots\times \Aut(T_d)$. 
And $T_j\triangleleft K$, $1\leq j\leq d$. 

Let $M_j=C_K(T_j)$. Then\[ \cdots\times T_{j-1}\times 1\times T_{j+1}\times \cdots\leq M_j\leq \cdots\times \Aut(T_{j-1})\times 1\times  \Aut(T_{j+1})\times \cdots \]
$M_j\triangleleft K$ and $K/M_j\lesssim \Aut(T_j)$ is almost simple with socle $T_j$.%\\A subgroup of $K$ is called \textbf{diagonal} if it is isomorphic to its projection on $\Aut(T_j)$ for each $1\leq j\leq d$.

\ 

Recall $H$ is a vertex-transitive solvable subgroup of $G$. 

Let $H^+=H\cap G^+$ and $H_j$ be the projection of $H^+\cap N$ on $T_j$, $1\leq j\leq d$.

Then $|H^+\cap N|$ divides $|H_1||H_2|\cdots|H_d|$.

\end{frame}

\begin{frame}{Exclude PA type}
\begin{lemma}[4.5]
Suppose $d\geq 2$. Then $\exists j\in\{1,2,...,d\}$ s.t. $M_j$ is transitive on $\Delta_1$ or $\Delta_2$; in particular, if $G^+$ is quasiprimitive on $\Delta_1$ or $\Delta_2$, then it is not of type PA.
\end{lemma}
\textbf{Proof. }\\
Assume $G^+$ is quasiprimitive of type PA on $\Delta_1$ or $\Delta_2$. \\
Then $\exists \mathcal{B}=\Omega^d$ a maximal block system s.t. $G^+\curvearrowright\mathcal{B}$ primitive by PA.\\
For $(w_1,w_2,...,w_d)\in\Omega^d$, $(x_1,x_2,...,x_d)\in M_j$, we have
\[(w_1,w_2,...,w_d)^{(x_1,x_2,...,x_d)}=(w_1^{x_1},w_2^{x_2},...,w_d^{x_d}).\]
From previous analysis, $x_j=1$. Then transitivity of $M_j$ implies $|\Omega|=1$.\\
\textcolor{blue}{Need to prove the transitivity of some $M_j$.}
\end{frame}

\begin{frame}
%Suppose no $M_j$ is transitive on both $\Delta_1$ and $\Delta_2$.
By lemma 4.4, $N\triangleleft G$ and $N_\alpha\neq 1$, $\forall \alpha\in V\Gamma$. By the following lemma,
\Lem2.5
we have $\Gamma$ is $N$-locally-primitive, hence $K$-locally-primitive since $N\leq K$.

\end{frame}


\begin{frame}
\begin{lemma}[2.4]
Let $\Gamma$ be a connected bipartite G-locally-primitive graph with G-orbits $\Delta_1$ and $\Delta_2$ on $V\Gamma$ and each $|\Delta_i|>1$. Suppose $\exists N\triangleleft G$ s.t. N is intransitive on $\Delta_1$ and $\Delta_2$. Then \footcite{GIUDICI2003analysing}\textsuperscript{,Lem 5.1}
\begin{enumerate}
	\item $\Gamma$ is a normal cover of $\Gamma_N$.
	\item $N$ is semiregular on $V\Gamma$, $G^{V\Gamma_N}\cong G/N$ and $G_\alpha\cong(G/N)_v$ for $\alpha\in V\Gamma$ and $v\in V\Gamma_N$.
	\item $\Gamma_N$ is $G/N$-locally-primitive. Futhermore, if $\Gamma$ is locally $(G,s)$-arc- transitive with $s\geq 2$, then $\Gamma_N$ is locally $(G/N,s)$-arc-transitive.
\end{enumerate}
\end{lemma}
If $M_j\triangleleft K$ is intransitive on both $\Delta_1$ and $\Delta_2$ for each $j=1,...,d$, \\
then $M_j$ is semiregular hence $M_j\cap K_\alpha=1$, and $K_\alpha\cong (K/M_j)_v\lesssim\Aut(T)$.
Furthermore, $K_\alpha$ is a diagonal subgroup, i.e. \textcolor{red}{Why?}
\[K_\alpha=\{(a,a,...,a)|a\in P\},\ P\leq\Aut(T).\]
\end{frame}


\begin{frame}
\[N_\alpha=N\cap K_\alpha=(T_1\times\cdots\times T_d)\cap K_\alpha=\{(a,a,...,a)|a\in P\cap T\}\lesssim T,\]
thus $|T|^{d-1}$ divides $|N:N_\alpha|=\textcolor{blue}{|\Delta_1|}$, 

\ 

$H^+\curvearrowright\Delta_1$ transitively $\implies$ $|T|^{d-1}$ divides $|H^+|=\textcolor{blue}{|H^+\cap K|}|H^+K/K|$.

$N\curvearrowright \Delta_1$ transitively $\implies$ \[K/N=K_\alpha N/N\cong K_\alpha/N_\alpha\cong P/(P\cap T)\cong PT/T\lesssim \Out(T).\]

$\therefore$ $|H^+\cap K|/\textcolor{blue}{|H^+\cap N|}$ divides $|\Out(T)|$.

$\because$ $|H^+\cap N|$ divides $|H_1\times\cdots\times H_d|$,

Therefore, \[|T|^{d-1}\text{ divides }|H_1\times\cdots\times H_d||\Out(T)||H^+K/K|.\]
\end{frame}


\begin{frame}
\textbf{Case: $H^+\not\leq K$: }


\end{frame}

\begin{frame}
\textbf{Case: $H^+\leq K$: }


\end{frame}




\begin{frame}{Quasiprimitive $G^+\curvearrowright \Delta_1$ and $\Delta_2$} 
\begin{lemma}[4.6]
$G^+$ is quasiprimitive on $\Delta_1$ and $\Delta_2$.
\end{lemma}
\textbf{Proof. } Assume $G^+\curvearrowright\Delta_1$ is NOT quasiprimitive.
\end{frame}

\begin{frame}
\textbf{Case (a): } $N_\alpha\cong T$.
\end{frame}


\begin{frame}
\textbf{Case (b): } $1\neq N_\alpha< T$.
\end{frame}

\begin{frame}
\textbf{Case (b.1): } L is nonsolvable.
\end{frame}

\begin{frame}
\textbf{Case (b.1): } L is solvable.
\end{frame}

\begin{frame}{Summary}
Recall hypothesis in the beginning of this section:
\begin{itemize}
	\item Let $\Gamma$ be a connected bipartite $(G,s)$-transitive graphs of val$\geq 3$, with bipartitions $\Delta_1$ and $\Delta_2$ and $s\geq 3$.
	\item Suppose $G$ is bi-quasiprimitive on $V\Gamma$ and contains a vertex-transitive solvable subgroup $H$. 
	\item Set $G^+=G_{\Delta_1}$, the setwise stabilizer of $G$ on $\Delta_1$, and $H^+=H\cap G^+$.
\end{itemize}

\begin{proposition}[4.7]
Under such hypothesis, either $\Gamma=\mathbf{K}_{n,n}$, or $G$ is an almost simple group and $G^+$ is quasiprimitive on both $\Delta_1$ and $\Delta_2$.
\end{proposition}
\proof{ If $G^+$ acts unfaithfully on $\Delta_1$ or $\Delta_2$, lemma 4.2 gives $\Gamma=\mathbf{K}_{n,n}$.\\
Faithful case: \\Lemma 4.3 shows either $G^+$ is not quasiprimitive on $\Delta_1$ or $\Delta_2$, or quasiprimitive on both with same type AS or PA.\\Lemma 4.6 exclude the former. Lemma 4.5 exclude PA in the latter.\\Finally lemma 4.4 implies G is AS.}
\end{frame}

\subsection{Almost simple groups}
\begin{frame}{$\soc(G)=T\leq G\leq \Aut(T)$}
By proposition 4.7, we may assume $G$ is almost simple with socle $T$, and $G^+$ is quasiprimitive on $\Delta_1$ and $\Delta_2$.

Set $G=T.\mathcal{O}$ and $G^+=T.\mathcal{O}'$, with $\mathcal{O}'<\mathcal{O}\leq \Out(T)$ and $|\mathcal{O}:\mathcal{O}'|=2$.

T is transitive on $\Delta_i$ $\implies$ $G=G_\alpha T$ $\implies$ $G_\alpha/T_\alpha\cong G_\alpha T/ T=G/T=\mathcal{O}$

By Frattini argument, $G=HG_\alpha$ and $G^+=H^+G_\alpha$. 

Both factorization have a solvable factor $H$, $H^+$.

\begin{lemma}[5.1]
$T\neq \PSL_2(q)$ with $q$ a prime power.
\end{lemma}
\proof{ Check the classification of connected 2-arc-transitive graphs admitting a two-dimensional linear automorphism group, see ref.\footcite{HASSANI1999twoarc}, in which the only 3-arc-transitive graph is the Petersen graph, a non-bipartite graph.}
\end{frame}

\begin{frame}{Case: $G_\alpha$ solvable}
\begin{lemma}[5.2]
If $G_\alpha$ solvable, then $T=\PSL_3(3)$ and $\Gamma=\PH(3,3^3)$ is 4-transitive of valency 4.
\end{lemma}
\end{frame}

\begin{frame}{Case: T alternating}
\begin{lemma}[5.3]
T is not an alternating simple group.
\end{lemma}
\end{frame}

\begin{frame}{Case: T sporadic}
\begin{lemma}[5.4]
T is not a sporadic simple group.
\end{lemma}
\end{frame}

\begin{frame}{Case: T classical }
\begin{lemma}[5.5]
If T is a classical simple group of Lie type, then $s\leq 4$, and one of the following is true.
\begin{enumerate}
	\item $T=\PSL_5(2)$, and $\Gamma\cong\GI(5,2,2)$.
	\item $T=\PSU_3(5)$, and $\Gamma\cong\HS_{50}^{(2)}$.
	\item $\Gamma$ is of valency $p^f+1$, $\PSL_3(p^f).2\leq G\leq\Aut(\PSL_3(p^f))$ and $\mathbb{Z}_p^{2f}:\SL_2(p^f)\triangleleft G_\alpha\leq P_1$ or $P_2$ where $P_1$ and $P_2$ are the stabilizers of T on a 1-dimension subspace and a 2-dimension subspace, respectively.
\end{enumerate}
\end{lemma}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{frame}{References}
\small
\printbibliography
\end{frame}



\end{document}


